Insecticide resistance evolution with mixtures and sequences : a model-based explanation.

### 2017-09-27 inst/documents/paper2/paper2_resistance_mechanisms_mixtures.Rmd
notes and paper2 tweaks

##### Conclusions
Our model provides an accessible description of the process of insecticide resistance evolution and how it is likely to respond to insecticide use. We provide a simple user-interface allowing further exploration (https://andysouth.shinyapps.io/MixSeqResist1). These tools can contribute to an improved discussion about operational decisions in insecticide resistance management.

@@

Parameter to increase  | increase favours mix or sequence | Mechanism
----------------------- | -------- | ---------------------------------------------
1. Effectiveness | mixture | Higher effectiveness gives faster resistance for sequence and slower resistance in mixture
2. Exposure | sequence | Higher exposure gives faster resistance for sequence and mixture but the greater effect on mixture favours sequence.
3. Dominance of restoration | neither | Higher dominance gives faster resistance in both sequences and mixtures such that the difference between them is not changed. 
4. Resistance restoration | neither | As for dominance of restoration. Higher resistance restoration gives faster resistance in both sequences and mixtures such that the difference between them is not changed.
5. Frequency  | neither | As for dominance and resistance restoration. Higher starting frequencies give faster resistance in both sequences and mixtures such that the difference between them is not changed.
6. Cost of resistance | mixture | Higher costs slow the evolution of resistance more in a mixture than when used in sequence (but with higher costs in a sequence there is a greater chance for resistance levels to decline for the insecticide not being used).

@@

![Figure 2. Screenshot of one online model user interface, accessible at : <https://andysouth.shinyapps.io/resistmob2/>. The user can modify values of the input parameters considered in this paper using simple sliders and run the model to get graphs of resulting resistance frequency over time. Two scenarios (A and B) can be run and the results viewed side by side. This makes it easy to explore the effect of changing individual inputs.](paper2_UI1.png)

>>>>

##### Conclusions
Our model provides an accessible description of the process of insecticide resistance evolution and how it is likely to respond to insecticide use. We provide a simple user-interface allowing further exploration (https://andysouth.shinyapps.io/resistmob2). These tools can contribute to an improved discussion about operational decisions in insecticide resistance management.

@@

Parameter to increase  | increase favours mix or sequence | Mechanism
----------------------- | -------- | ---------------------------------------------
1. Effectiveness | mixture | Higher effectiveness gives faster resistance for sequence and slower resistance in mixture
2. Exposure | sequence | Higher exposure gives faster resistance for sequence and mixture but the greater effect on mixture favours sequence.
3. Dominance of restoration | neither | Higher dominance gives faster resistance in both sequences and mixtures such that the difference between them is not changed. 
4. Resistance restoration | neither | As for dominance of restoration. 
5. Frequency  | neither | As for dominance and resistance restoration. 
6. Cost of resistance | mixture | Higher costs slow the evolution of resistance more in a mixture than when used in sequence (but with higher costs in a sequence there is a greater chance for resistance levels to decline for the insecticide not being used).

@@

![Figure 2. Screenshot of one online model user interface, accessible at : <https://andysouth.shinyapps.io/resistmob2>. The user can modify values of the input parameters considered in this paper using simple sliders and run the model to get graphs of resulting resistance frequency over time. Two scenarios (A and B) can be run and the results viewed side by side. This makes it easy to explore the effect of changing individual inputs.](paper2_UI1.png)
